Methodology for Assessing the State of the Practice for Domain X

### 2020-05-15 StateOfPractice/Methodology/Methodology.tex
merged sections 7.5 and 7.5

\subsection {Procedure}
\begin {enumerate}
%\item Write research questions
%\item Prepare logistic details(location, time table, recording setup, moderators etc)
%\item Prepare survey questions
%\item Select a list of projects
%\item Design the tasks for the study subjects to perform (tasks can be defined based on user category, at least one task to modify the software)
%\item Select participants

\item Survey participants to collect pre-experiment data
\item Perform tasks
\item Observe the study subjects (take notes, record sessions, watch out for body languages and verbal cues)
\item Survey the study subjects to collect feedback
\item Prepare experiment report
\item Perform pairwise comparison analysis
\item Prepare analysis report
\end {enumerate}

\subsection{Empirical Measures}
 \begin {enumerate}
 \item Qualitative/Quantitative
 \item Pairwise Comparison methodology needs to be described
 \item Measure time to complete a task and compare actual with expected time of completion
 \item From a list of given tasks, measure how many tasks were completed correctly
 \item Learnability
 \item Efficiency
 \item Memorability
 \item Errors
 \item Satisfaction
 \item Heuristic evaluation: Experts go through the interface to identify elements that violate usability heuristics.Popular because of its low cost and low time commitment
\end {enumerate}

@@

\subsection{Defining usability tasks}
Below are the requirements to be used in defining usability tasks
\item Tasks should take no more than 2 hours for completion - review timing
\item Tasks should be defined for different three different levels of participant: Expert, intermediate and novice (These 3 groups of users should be defined)
\item Tasks should be defined based on 3 difficulty levels : Difficult, Medium and easy (Difficulty levels should be defined) 
\subsection{Task selection criteria}
\item Commonly performed tasks (applicable to all the selected software)
\item Task that would/should generate errors messages or error codes
\item Tasks to check standards and conventions
\item Tasks that should provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to End tasks that require users to go through sequential or hierarchical steps.
\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
\item Tasks that should provide users with feedback
\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
\item Tasks to verify if the system is capable of preventing and /or reversing errors
\item Tasks that can lead the user to use help or documentation
\item Task to modify the source code

>>>>

\subsection {Procedure}
\begin {enumerate}
%\item Select a list of projects
%\item Write research questions
%\item Prepare logistic details(location, time table, recording setup, moderators etc)
%\item Prepare survey questions
%\item Design the tasks for the study subjects to perform (tasks can be defined based on user category, at least one task to modify the software)
%\item Select participants

\item Survey participants to collect pre-experiment data
\item Participants perform tasks
\item Observe the study subjects (take notes, record sessions, watch out for body languages and verbal cues)
\item Survey the study subjects to collect feedback (post experiment interview)
\item Prepare experiment report
\item Perform pairwise comparison analysis
\item Prepare analysis report
\end {enumerate}

%\subsection{Empirical Measures}
% \begin {enumerate}
% \item Qualitative/Quantitative
% \item Pairwise Comparison methodology needs to be described
% \item Measure time to complete a task and compare actual with expected time of completion
% \item From a list of given tasks, measure how many tasks were completed correctly
% \item Learnability
% \item Efficiency
% \item Memorability
% \item Errors
% \item Satisfaction
% \item Heuristic evaluation: Experts go through the interface to identify elements that violate usability heuristics.Popular because of its low cost and low time commitment
%\end {enumerate}

@@

\subsection{Task selection criteria}
Below are the criteria to be used in defining usability experiment tasks
\begin {enumerate}
\item Tasks should take no more than 2 hours(in one sitting) for completion.
\item Tasks should be defined for different three different levels of participant: Expert, intermediate and novice (These 3 groups of users should be defined)
\item Tasks should be defined based on 3 difficulty levels : Difficult, Medium and easy (Difficulty levels should be defined) 
\item What are the most common tasks that users perform (these applies to all selected projects collectively) on the software application.
\item Task that would generate errors messages or error codes
\item Tasks to check standards and conventions
\item Tasks that provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to end tasks that require users to go through sequential or hierarchical steps.
\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
\item Tasks that provide users with feedback.
\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
\item Tasks to verify if the system is capable of preventing and /or reversing errors
\item Tasks that would lead the user to use help or documentation
%\item Task to modify the source code
